%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Peer-reviewed Journals}

\begin{cvpubs}
    \cvpub{Yang, J., Teran, C., {\textbf{Battocchio, A.F}.}, Bertellotti, E., and Wrzesinski, S. (2021). “Building Brand Authenticity on Social Media: The Impact of Instagram Ad Model Genuineness and Trustworthiness on Perceived Brand Authenticity and Consumer Responses. ”\textit{Journal of Interactive Advertising}. DOI: 10.1080/15252019.2020.1860168}

    \cvpub{Yang, J. and  \textbf{Battocchio, A.F.} (2020). “Effects of Transparent Brand Communication on Perceived Brand Authenticity and Consumer Responses.” \textit{Journal of Product \& Brand Management}. Vol. ahead-of-print No. ahead-of-print.\\ DOI: 10.1108/JPBM-03-2020-2803}
\end{cvpubs}

%-------------------------------------------------------------------------------
%	BOOK CHAPTERS
%-------------------------------------------------------------------------------
\cvsection{Peer-reviewed Book Chapters}

\begin{cvpubs}
    \cvpub{\textbf{Battocchio, A.F.}, Wells, C., Vraga, E., Thorson, K., Edgerly, S., and Bode, L. (In Press) “Gen Z’s civic engagement: News use, politics, and cultural engagement.” in \textit{Handbook of Digital Politics} }
    
    \cvpub{\textbf{Battocchio, A.F.}, Bode, L., Wells, C., Vraga, E., Thorson, K., and Edgerly, S. (In Press). “Gen Z’s civic engagement: Civic skills, political expression, and identity .” in \textit{Handbook of Digital Politics} }
\end{cvpubs}

%-------------------------------------------------------------------------------
%	CONFERENCE PAPERS, POSTERS, PRESENTATIONS
%-------------------------------------------------------------------------------
\cvsection{Peer-reviewed Conference Papers, Posters, and Presentations}

\begin{cvpubs}
	
    \cvpub{\textbf{Battocchio, A. F.,} Thorson, K., Hiaeshutter‑Rice, D., Smith, M., Chen, Y., Edgerly, S., Cotter, K., Denzin, K., Choung, H., Dong, C., Moldagaliyeva, M., Etheridge, C., Kohlmeier, S., and Werth, L. (2022). “Localizing social justice stories: Social media and local civic information infrastructure in six midwestern United States communities.” Presented in the Communication Theory and Methods Division of the Association for Education in Journalism and Mass Communication(AEJMC), Detroit, MI, August 5, 2022.  }

    \cvpub{Chen, Y., Choung, H., \textbf{Battocchio, A.F.}, Hiaeshutter-Rice, D., Smith, M., Draeger, M., Dong, C., and Xiao, A. (2022). “Discursive Opportunity Structure: The evolutions of racial justice discourses by local community organizations on Facebook.” Presented in the Communication Theory and Methods Division of the Association for Education in Journalism and Mass Communication(AEJMC), Detroit, MI, August 5, 2022.}
    
	\cvpub{\textbf{Battocchio, A.F.} and Smith, M. (2022). "Reaching the Rust Belt: Exploring identity and intergroup threat in 2020 election speeches." Presented in the Political Communication Division of the Association for Education in Journalism and Mass Communication(AEJMC), Detroit, MI, August 3, 2022.}
    
	\cvpub {\textbf{Battocchio, A.F. }(2021) “Hyperlocal affective polarization: Remixing rural understanding." Presented in the Communication Theory and Method (CT\&M) Division of the Association for Education in Journalism and Mass Communication (AEJMC), Virtual Conference, August 6, 2021.} \scriptsize{\textit{*}awarded CT\&M Top Student Paper: Second Place}
    
    \cvpub {Yang, J., Bertellotti, E., \textbf{Battocchio, A.F.}, and Teran, C. (2021) “Do Good and Be ‘Liked'": Corporate messaging on social media during COVID-19 and consumer responses." Presented in the Advertising Division of the Association for Education in Journalism and Mass Communication(AEJMC), Virtual Conference, August 7, 2021.}
    
    \cvpub {\textbf{Battocchio, A. F.}, Etheridge, C., Thorson, K., Moldagaliyeva, M., Hiaeshutter-Rice, D., Dong, C., Cotter, K., Chen, Y., Kohlmeier, S., Denzin, K., Draeger, M. and Edgerly, S. (2021). “A systematic method of cataloging civic information infrastructure." Presented in the Communication Theory and Method Division of the Association for Education in Journalism and Mass Communication (AEJMC) annual conference, Virtual Conference, August 5, 2021.}

    \cvpub {Thorson, K. and {\textbf{Battocchio, A.F}.} (2021). “Change is the only constant: Young adults as platform architects and the consequences for news”. Presented at the Mass Communication and Society Division of the Association for Education in Journalism and Mass Communication (AEJMC) annual conference, Virtual Conference, August 7, 2021.} \scriptsize{\textit{*}awarded 2021 News Audience Research Paper Award}

    \cvpub{Yang, J. and \textbf{Battocchio, A.F. }(2020). “Effects of transparent brand communication on perceived brand authenticity and consumer responses.” Presented at the Association for Education in Journalism and Mass Communication (AEJMC) annual conference, Virtual Conference, August 6-9, 2020. }
    
    \cvpub{Yang, J., Teran, C., \textbf{Battocchio, A.F}., Bertellotti, E., and Wrzesinski, S. (2020). “Building brand authenticity on social media: The impact of Instagram ad model genuineness and trustworthiness on perceived brand authenticity and consumer responses.” Presented at the Association for Education in Journalism and Mass Communication (AEJMC) annual conference, Virtual Conference, August 6-9, 2020.}
    
    \cvpub{\textbf{Battocchio, A.F.}(2019). “Advertising and ethics: Theme and community segregation on Chicago’s Rapid Transit System.” Presented at the Association for Education in Journalism and Mass Communication (AEJMC) annual conference, Toronto, ON, August 8, 2019. }

\end{cvpubs}
%-------------------------------------------------------------------------------
%	SYMPOSIUMS AND CONFERENCE PANELS
%-------------------------------------------------------------------------------
\cvsection{Peer-reviewed Conference Panels and Symposiums}

\begin{cvpubs}
    \cvpub{\textbf{Battocchio, A.F.} (2022) Panel titled "Graduate Student and Early Career Professional Development and Network Building Panel" (organized by Claire M. Segijn) to be presented at the Association for Education in Journalism and Mass Communication (AEJMC) annual conference, Detroit, MI, August 4, 2022}
    
    \cvpub{Thorson, K., and \textbf{Battocchio, A.F.} (2022). “Combining interviews with digital trace data for rich understanding of political content exposure across algorithmically curated platforms.” Panel titled “Caught the bull by the horns! New tools for measuring media use in a changing media landscape” (organized by Peter Neijens, Judith Moeller, Theo Araujo, and Claes de Vreese). Presented at the 72nd Annual International Communication Association Conference, Paris, France, May 30, 2022}
    
    \cvpub{Thorson, K., and \textbf{Battocchio, A.F.} (2022). “Platform repertoires and perceptions of information quality among American young adults.” Panel titled “Everyday Misinformation on Private Social Media: Relationality, Affordances, and Norms in the Traversal of Interpersonal and Public Networks” (organized by Andrew Chadwick). Presented at the 72nd Annual International Communication Association Conference, Paris, France, May 29, 2022}
    
    \cvpub{\textbf{Battocchio, A.F.} (2022). “Opportunities Lost to the Pandemic: Guiding students through Disrupted Educational Trajectories.”  Panel titled “Un-Conference: Bringing Experiences to the Front.” (organized by  Saleem Alhabash, Teresa Mastin, Gordon Miracle, Karen Mallia, Cynthia Frisby, and Wei-Na Lee). To be presented at the American Academy of Advertising(AAA) preconference “Diversity, Equity, and Inclusion in Action: Advertising Research, Teaching, and Practice”, March 26, 2022}

   \cvpub{\textbf{Battocchio, A.F.}, Thorson, K., Hiaeshutter‑Rice, D., Smith, M., Chen, Y., Edgerly, S., Cotter, K., Denzin, K., Choung, H., Dong, C., Moldagaliyeva, M., Etheridge, C., Kohlmeier, S., and Werth, L.(2021). “Local information infrastructure and the distribution of COVID-19 information on Facebook in six Great Lakes communities.” Panel titled “Media Deserts, Platforms, and Community Civic Infrastructure: Tales from the Great Lakes States During COVID-19” (organized by Usher, N., Russel, A., and Holcomb, J.) To be presented at the  National Communication Association’s annual meeting, Seattle, WA, November 18-21, 2021}
   
   \cvpub{\textbf{Battocchio, A.F.} (2021). “Take only photos, leave only digital traces: Listening to community narratives in urbex photography”. Panel titled “Rhetorical Rhythms of the City; A Dialogic Engagement with Ethics in Urban Contexts” (organized by Carmack, P.) Presented at the Urban Communication Ethics conference, Virtual Conference, June 6-8, 2021.}
   
    \cvpub{Morris, P.K. and \textbf{Battocchio, A.F}. (2019).“Outdoor advertising heats Up: Transforming digital signage and ethical issues.” Presented at Ninth Symposium on Digital Ethics, Center for Digital Ethics and Policy, Loyola University, Chicago, IL, November 7-8, 2019. }
    
    \cvpub{\textbf{Battocchio, A.F.} (2019). "Advertising and ethics: Theme segmentation and community segregation on Chicago's Rapid Transit System." Presented at the Undergraduate Research and Engagement Symposium, Loyola University, Chicago, IL, April 13, 2019.}
    
%-------------------------------------------------------------------------------
%	BOOK REVIEWS
%-------------------------------------------------------------------------------
\cvsection{Commissioned and Peer-adjudicated Book Reviews}

\begin{cvpubs}
    \cvpub{\textbf{Battocchio, A.F.} (Forthcoming). Review of Hirsh, Richard F. \textit{Powering American Farms: The Overlooked Origins of Rural Electrification}. H-Sci-Med-Tech, H-Net Reviews}
\end{cvpubs}

% %---------------------------------------------------------
